Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-09 paper-2023-acsos-pulverization.tex
stub an abstract

\begin{abstract}
TBD
\end{abstract}

@@

\section{Introduction}

\nocite{*}

>>>>

\begin{abstract}
In recent years, we witnessed a radical change in the deployed form of distributed systems.
%
Modern applications are designed to be executed on very diverse devices
and to be deployed on heterogeneous infrastructures,
ranging from cloud servers to mobile and IoT devices.
%
De facto, complex distributed computation is happening across a cloud-edge continuum composed of heterogeneous devices and infrastructures.
%
The availablity of such an infrastructure opens to new possibilities in terms of better resource utilisation and performance,
but also poses new challenges to the application designer,
as the application must be conceived to be able to adapt its deployment to changing conditions.
%
In this paper we present a framework for the development of distributed systems
based on the concept of \emph{pulverisation},
which is meant to neatly separate business logic and deployment concerns,
allowing applications to be defined independent of the infrastructure they will execute upon.
%
The framework is based on a domain-specific language capturing,
in a declarative fashion,
the concepts composing a pulverised application and any potential target network,
also allowing for the specification of reconfiguration policies.
%
The framework, implemented in Kotlin multiplatform and available as open source,
is then evaluated in a small-scale real-world demo and in a city-scale simulated scenario.
\end{abstract}

@@

\section{Introduction}\label{sec:introduction}

\begin{itemize}
    \item need for deployment-independent specs
    \item need for runtime reconfiguration (achieve QoS in face of changing conditions --- green computing?)
    \item declarativity over imperative approaches (note: can be compared with the trend in general softeng/build systems)
\end{itemize}

+ related work

\section{A framework for declarative runtime reconfiguration}\label{sec:contribution}

\subsection{Domain model}

\subsection{Domain-specific language}

\subsection{Implementation details}

Also mention that is multiplatform

\section{Evaluation}\label{sec:evaluation}

\subsection{Small scale: crowd alert}

\subsection{Large scale: smart city application}
\cite{PianiniJOS2013}

\section{Conclusion and future work}\label{sec:conclusion}

global policies
